\bf Tearing Mode Dynamics in Tokamak Plasmas

### 2021-11-26 Documentation/TearingModeTheory.tex
Started isolated islands

\subsection{Asymptotic Matching}
It is convenient to parametrize the error-field in terms of the static current, $I_c$, that must be run through the magnetic
field-coil introduced in Section~\ref{sfc} in order to generate it. Setting $d/dt=0$ in Equations~(\ref{e202}) and (\ref{e203}),
we get
\begin{equation}\label{e400}
{\mit\Delta\hat{\Psi}}_s = {\mit\Delta}_{nw}\,\hat{\mit\Psi}_s+\tilde{I}_c,
\end{equation}
where
\begin{equation}
{\mit\Delta}_{nw} = {\mit\Delta}_{pw} + \frac{E_{sw}^{\,2}}{(-\tilde{E}_{ww})}
\end{equation}
is the (real) tearing stability index in the absence of a wall, ${\mit\Delta}_{pw}= E_{ss}$ is the
(real) tearing stability index in the presence of a perfectly conducting wall at $r=r_w$, and
\begin{equation}
\tilde{I}_c =\left(\frac{{\mit\Delta}_{nw} - {\mit\Delta}_{pw}}{E_{sw}}\right)\left(
\frac{r_w}{r_c}\right)^m\left(\frac{\mu_0\,I_c}{R_0\,B_z}\right).
\end{equation}
Here, the plasma-wall coupling parameter, $E_{sw}>0$, is defined in Section~\ref{resistive}. We expect $0>{\mit\Delta}_{nw}>
{\mit\Delta}_{pw}$ because the plasma is assumed to be tearing stable, and $\tilde{E}_{ww}<0$.

@@

Equations~(\ref{e469})--(\ref{e473}) must be solved subject to the boundary conditions
\begin{align}
{\mit\Psi}&\rightarrow \frac{X^{2}}{2} + \cos\zeta,\label{e483}\\[0.5ex]
{\mit\Phi} &\rightarrow v\,X +\frac{ s\,v'\,X^{2}}{2},\label{e484}\\[0.5ex]
{\cal N}&\rightarrow X,\label{e486}\\[0.5ex]
{\cal V}&\rightarrow 0,\label{e486a}\\[0.5ex]
{\cal J}& \rightarrow 0,\label{e487}
\end{align}
as $|X|\rightarrow\infty$.  Here,
\begin{align}
v(T) &= \frac{\omega-\omega_E}{\omega_\ast},\label{e488}\\[0.5ex]
v'(T) &= -\frac{\hat{w}}{2\,\omega_\ast}\left[r\,\frac{d\omega_E}{dr}\right]_{r_{s-}}^{r_{s+}}.
\end{align}
In the following, it is assumed that $v\sim{\cal O}(1)$ and $|v'|\ll 1$. Note that ${\mit\Psi}$, ${\mit\Phi}$, ${\cal N}$, ${\cal V}$, and ${\cal J}$ are all ${\cal O}(1)$ quantities.
Note, further,  that the boundary conditions (\ref{e483})--(\ref{e487}),
as well as the symmetry of the rescaled four-field equations,  (\ref{e469})--(\ref{e473}), ensure that ${\mit\Psi}$, ${\cal V}$, and
${\cal J}$ are even functions of $X$, whereas ${\mit\Phi}$ and ${\cal N}$ are odd functions.

\subsection{Ordering Scheme}
In the following, the dimensionless parameters $\epsilon_d$, $\epsilon_\beta$, $\epsilon_n$, $\epsilon_\eta$, $\epsilon_\chi$,
and $\epsilon_D$ are all assumed to be of similar size, but much smaller than unity. The orderings $\epsilon_n\ll 1$ and $\epsilon_\beta\ll 1$
are consistent with the standard large-aspect ratio, low-$\beta$ orderings used to describe conventional tokamak
plasmas (Freidberg 1987). As will become apparent, the ordering $\epsilon_d\ll 1$ ensures that the island chain is
sufficiently wide that ion acoustic waves propagating parallel to the magnetic field are able to smooth out any
variations in the normalized electron number density, ${\cal N}$, around magnetic flux-surfaces (Scott, Hassam \& Drake 1985). The orderings $\epsilon_\eta\ll 1$, $\epsilon_\chi\ll 1$, and $\epsilon_D\ll 1$ ensure that the island
chain is sufficiently wide that the perpendicular diffusion of magnetic flux, momentum, and particles are not dominant
effects in the rescaled four-field equations. We shall also assume that $w/w_c\sim{\cal O}(1)$. In other words, the
island chain is sufficiently wide for the parallel diffusion of particles to compete with perpendicular diffusion.

@@

Finally, to lowest order in $\epsilon_d$, Equation~(\ref{e470}) yields
\begin{equation}\label{e509}
\{{\cal J}_0,{\mit\Omega}\} = -\partial_X\!\left({\mit\Phi}_0+\frac{{\cal N}_0}{1+\tau}, \partial_X {\mit\Phi}_0\right)=
\frac{1}{2}\left\{d_{\mit\Omega}\!\left[M\left(M+\frac{L}{1+\tau}\right)\right]X^2, {\mit\Omega}\right\},
\end{equation}
where use has been made of Equations~(\ref{e498}), (\ref{e501}), and (\ref{e505}). Moreover, $d_{\mit\Omega}\equiv
d/d{\mit\Omega}$.

@@

\subsection{Fluid Velocities}\label{s8.6}
The flux-surface functions $M({\mit\Omega},T)$ and $L({\mit\Omega},T)$ are directly related to the lowest-order perpendicular
velocities of the various fluid species in the island rest frame. In fact, as is clear from Sections~\ref{s4.2}, \ref{s4.3}, and \ref{s8.2}, 
\begin{align}
V_\theta(x,\zeta,T) &= -\frac{\omega_\ast}{m}\,x\,M({\mit\Omega},T),\\[0.5ex]
V_{\theta\,i}(x,\zeta,T)& = -\frac{\omega_\ast}{m}\,x\,Y_i({\mit\Omega},T)\\[0.5ex]
V_{\theta\,e}(x,\zeta,T)& = -\frac{\omega_\ast}{m}\,x\,Y_e({\mit\Omega},T),
\end{align}
where
\begin{align}
Y_i({\mit\Omega},T)&= M+\left(\frac{1}{1+\tau}\right)L,\label{e518}\\[0.5ex]
Y_e({\mit\Omega},T)&= Y_i- L.
\end{align}
Here, $V_\theta$, $V_{\theta\,i}$, and $V_{\theta\,e}$ refer to velocity components of the MHD, ion, and
electron fluid, respectively. Note that $Y_i$ and $Y_e$ are both zero inside the magnetic separatrix of the island chain.

@@

We need to evaluate Equation~(\ref{e471}) to first order in $\epsilon_d$ in order to include the perpendicular transport term. Doing so,
we obtain
\begin{equation}
0= \epsilon_d\,\{{\cal V}_1, {\mit\Omega}\} + \epsilon_D\,(X^2\,d_{\mit\Omega} L + L),
\end{equation}
where use has been made of Equations~(\ref{e498}), (\ref{e500}),  and (\ref{e501}). The flux-surface average of the
previous equation yields
\begin{equation}
\langle X^2\rangle\,d_{\mit\Omega} L +\langle 1\rangle\,L = 0,
\end{equation}
where use has been made of Equation~(\ref{e5111}). 
We can solve the previous equation, subject to the boundary condition (\ref{e502}), to give
\begin{equation}\label{e526}
L({\mit\Omega})=\left\{
\begin{array}{llr}
0&&-1\leq {\mit\Omega}\leq 1\\[0.5ex]
1/\langle X^2\rangle&~~&{\mit\Omega}>1
\end{array}\right..
\end{equation}
Here, we have taken into account the previously mentioned fact that $L=0$ within the island separatrix.

We need to evaluate Equation~(\ref{e470}) to first order in $\epsilon_d$ in order to include the perpendicular transport term. Doing so,
we obtain
\begin{equation}\label{e528a}
0 =\epsilon_d\,\{{\cal J}_1,{\mit\Omega}\} +\epsilon_\chi\,X\,d_{{\mit\Omega}}\!\left[d_{\mit\Omega}\!\left(X^3\,d_{\mit\Omega} Y_i\right)\right].
\end{equation}
where use has been made of Equations~(\ref{e498}), (\ref{e500}), (\ref{e501}), (\ref{e503}), (\ref{e505}), and (\ref{e518}). The flux-surface average of the previous equation yields 
\begin{equation}
d_{\mit\Omega}^{\,2}\!\left(\langle X^4\rangle\,d_{\mit\Omega} Y_i\right)= 0.
\end{equation}
We can solve the previous equation, subject to the boundary conditions (\ref{e502}) and (\ref{e506}), to give
\begin{equation}\label{e530}
Y_i({\mit\Omega},T)=\frac{v'(T)}{\int_1^\infty \!\frac{d{\mit\Omega}}{\langle X^4\rangle}}\left\{
\begin{array}{llr}
0&&-1\leq {\mit\Omega}\leq 1\\[0.5ex]
\int_1^{\mit\Omega}\! \frac{d{\mit\Omega}'}{\langle X^4\rangle}&~~&{\mit\Omega}>1
\end{array}\right.
\end{equation}
(Fitzpatrick \& Waelbroeck 2005).
Here, we have made use of the fact that $Y_i=0$ within the magnetic separatrix of the island chain. We have also demanded that the ion
fluid velocity, and, hence, the function $Y_i$,  be continuous across the separatrix, because the ion fluid possesses finite perpendicular viscosity. 
Note, however, that the discontinuity in the function $L({\mit\Omega})$ across the separatrix [see Equation~(\ref{e526})] implies that the
MHD and electron fluid velocities are  discontinuous across the separatrix. (See Section~\ref{s8.6}.)

In the limit ${\mit\Omega}\gg 1$, the previous equation yields
\begin{equation}
Y_i\simeq v' -\left. \frac{v'}{\sqrt{2\,{\mit\Omega}}}\right/\int_1^\infty \frac{d{\mit\Omega}}{\langle X^4\rangle}.
\end{equation}
Hence, it follows from Equations~(\ref{e518}) and (\ref{e526}) that
\begin{equation}
M\simeq v' -\left. \frac{v'}{\sqrt{2\,{\mit\Omega}}}\right/\int_1^\infty \frac{d{\mit\Omega}}{\langle X^4\rangle} -\left(\frac{1}{1+\tau}\right)
\frac{1}{\sqrt{2\,{\mit\Omega}}}
\end{equation}
in the same limit. A comparison with Equation~(\ref{e506}) reveals that
\begin{equation}
v = -\frac{1}{1+\tau} - v'\left/\int_1^\infty \frac{d{\mit\Omega}}{\langle X^4\rangle}\right.,
\end{equation}
or 
\begin{equation}\label{e534}
\omega = \omega_{\perp\,i} -v'\,\omega_\ast\left/\int_1^\infty \frac{d{\mit\Omega}}{\langle X^4\rangle}\right.,
\end{equation}
where
\begin{equation}
\omega_{\perp\,i} = \omega_E + \omega_{\ast\,i},
\end{equation}
and use has been made of Equations~(\ref{omegai}), (\ref{omega}), and (\ref{e488}).

@@

Equations~(\ref{e528a}) and (\ref{e543}) can be combined to give (Fitzpatrick \& Waelbroeck 2005)
\begin{align}
{\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right) &=\frac{4\,\epsilon_\beta\,\epsilon_d\,\epsilon_\chi}{\hat{w}}\int_1^\infty
\left\langle X^{2}\,d_{\mit\Omega}\!\left[d_{\mit\Omega}(X^3\,d_{\mit\Omega}Y_i)\right]\right\rangle d{\mit\Omega}\nonumber\\[0.5ex]
&=\frac{4\,\epsilon_\beta\,\epsilon_d\,\epsilon_\chi}{\hat{w}}\int_1^\infty d_{\mit\Omega}\!\left(-\langle X\rangle\,Y_i
+2\,\langle X^3\rangle\,d_{\mit\Omega} Y_i + \langle X^5\rangle\,d_{\mit\Omega}^{\,2} Y_i\right)d{\mit\Omega}\nonumber\\[0.5ex]
&= \frac{4\,\epsilon_\beta\,\epsilon_d\,\epsilon_\chi}{\hat{w}}\,\lim_{\mit\Omega\rightarrow\infty}\left(-\langle X\rangle\,Y_i
+2\,\langle X^3\rangle\,d_{\mit\Omega} Y_i + \langle X^5\rangle\,d_{\mit\Omega}^{\,2} Y_i\right),
\end{align}
where use has been made of the facts that $Y_i$ is zero inside the island separatrix, and $Y_i$ is continuous across the separatrix.
Combining the previous equation with Equation~(\ref{e530}), we obtain (Fitzpatrick \& Waelbroeck 2005)
\begin{equation}\label{e545}
{\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)  =- \frac{4\,\epsilon_\beta\,\epsilon_d\,\epsilon_\chi\,v'}{\hat{w}}.
\end{equation}
Finally, the previous equation can be combined with Equation~(\ref{e534}) to give
\begin{equation}
\omega=\omega_{\perp\,i} + I_1\left(\frac{\tau_\varphi}{\tau_H^{\,2}}\right)\left(\frac{W}{r_s}\right)^5{\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right),
\end{equation}
where
\begin{equation}
I_1 = 2^{-12}\left/\int_1^{\infty} \frac{d{\mit\Omega}}{\langle X^4\rangle}\right. =3.584\times 10^{-4}. 
\end{equation}
Here, use has been made of Equations~(\ref{e479}), (\ref{e480}), and (\ref{e482}).

Equations~(\ref{e524a}) and (\ref{e542}) can be combined to give
\begin{align}
{\rm Re}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)&= \frac{2\,\epsilon_\beta\,\epsilon_d}{\hat{w}}
\int_{1+}^\infty d_{\mit\Omega}(M\,Y_i)\left\langle\widetilde{X^2}\,\cos\zeta\right\rangle d{\mit\Omega}
+\frac{4}{\epsilon_\eta\,\hat{w}}\,\frac{d(\ln \hat{w}^2)}{dT}\int_{-1}^\infty \frac{\langle \cos\zeta\rangle^2}{\langle 1\rangle}\,d{\mit\Omega}
\end{align}
Making use of Equations~(\ref{e518}), (\ref{e526}), and (\ref{e530}), the previous equation yields
\begin{align}
{\rm Re}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)&= -\frac{2\,\epsilon_\beta\,\epsilon_d\,v'}{(1+\tau)\,\hat{w}}
\int_1^\infty d_{\mit\Omega}\!\left(\frac{F_i}{\langle X^2\rangle}\right)\left\langle\widetilde{X^2}\,\cos\zeta\right\rangle d{\mit\Omega}
\nonumber\\[0.5ex]&\phantom{=}+\frac{4}{\epsilon_\eta\,\hat{w}}\,\frac{d(\ln \hat{w}^2)}{dT}\int_{-1}^\infty \frac{\langle \cos\zeta\rangle^2}{\langle 1\rangle}\,d{\mit\Omega},\label{e547}
\end{align}
where
\begin{equation}
F_i({\mit\Omega})=\left.\int_1^{\mit\Omega}\frac{d{\mit\Omega}'}{\langle X^4\rangle}\right/\int_1^\infty\frac{d{\mit\Omega}}{\langle X^4\rangle}
\end{equation}
Here, we have neglected terms that are quadratic in the small parameter $v'$. Finally, Equations~(\ref{e545}) and (\ref{e547})
can be combined to give (Waelbroeck \& Fitzpatrick 1997)
\begin{equation}
{\rm Re}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)= I_2\,\tau_R\,\frac{d}{dt}\!\left(\frac{W}{r_s}\right)
- I_3\left(\frac{c_\beta}{1+\tau}\right)\left(\frac{d_\beta}{r_s}\right)\left(\frac{L_s}{L_n}\right)\left(\frac{\tau_\varphi}{\tau_H}\right)\left(\frac{W}{r_s}\right)^2 {\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right),
\end{equation}
where
\begin{align}
I_2 &= 2\int_{-1}^\infty \frac{\langle \cos\zeta\rangle^2}{\langle 1\rangle}\,d{\mit\Omega} =0.8227,\\[0.5ex]
I_3&= 2^{-6}\int_1^\infty d_{\mit\Omega}\!\left(\frac{F_i}{\langle X^2\rangle}\right)\left(\langle X^4\rangle - \frac{\langle X^2\rangle^2}{\langle 1\rangle}\right)d{\mit\Omega} = 3.055\times 10^{-3}.
\end{align}
Here, use has been made of Equations~(\ref{e317a}), (\ref{e318a}), (\ref{e481}), and (\ref{e482}).

>>>>

\subsection{Asymptotic Matching}
It is convenient to parametrize the error-field in terms of the static current, $I_c$, that must be run through the magnetic
field-coil introduced in Section~\ref{sfc} in order to generate it. Setting $d/dt=0$ in Equations~(\ref{e202}) and (\ref{e203}),
we get
\begin{equation}\label{e400}
{\mit\Delta\hat{\Psi}}_s = {\mit\Delta}_{nw}\,\hat{\mit\Psi}_s+\tilde{I}_c,
\end{equation}
where
\begin{equation}
{\mit\Delta}_{nw} = {\mit\Delta}_{pw} + \frac{E_{sw}^{\,2}}{(-\tilde{E}_{ww})}
\end{equation}
is the (real) tearing stability index in the absence of a wall, 
\begin{equation}\label{epw}
{\mit\Delta}_{pw}= E_{ss}
\end{equation}
 is the
(real) tearing stability index in the presence of a perfectly conducting wall at $r=r_w$, and
\begin{equation}
\tilde{I}_c =\left(\frac{{\mit\Delta}_{nw} - {\mit\Delta}_{pw}}{E_{sw}}\right)\left(
\frac{r_w}{r_c}\right)^m\left(\frac{\mu_0\,I_c}{R_0\,B_z}\right).
\end{equation}
Here, the plasma-wall coupling parameter, $E_{sw}>0$, is defined in Section~\ref{resistive}. We expect $0>{\mit\Delta}_{nw}>
{\mit\Delta}_{pw}$ because the plasma is assumed to be tearing stable, and $\tilde{E}_{ww}<0$.

@@

Equations~(\ref{e469})--(\ref{e473}) must be solved subject to the boundary conditions
\begin{align}
{\mit\Psi}&\rightarrow \frac{X^{2}}{2} + \cos\zeta,\label{e483}\\[0.5ex]
{\mit\Phi} &\rightarrow v\,X +\frac{ s\,v'\,X^{2}}{2},\label{e484}\\[0.5ex]
{\cal N}&\rightarrow X,\label{e486}\\[0.5ex]
{\cal V}&\rightarrow 0,\label{e486a}\\[0.5ex]
{\cal J}& \rightarrow 0,\label{e487}
\end{align}
as $|X|\rightarrow\infty$.  Here,
\begin{align}
v(T) &= \frac{\omega-\omega_E}{\omega_\ast},\label{e488}\\[0.5ex]
v'(T) &= -\frac{\hat{w}}{2\,\omega_\ast}\left[r\,\frac{d\omega_E}{dr}\right]_{r_{s-}}^{r_{s+}}.\label{e489}
\end{align}
Note that ${\mit\Psi}$, ${\mit\Phi}$, ${\cal N}$, ${\cal V}$, and ${\cal J}$ are all ${\cal O}(1)$ quantities.
Note, further,  that the boundary conditions (\ref{e483})--(\ref{e487}),
as well as the symmetry of the rescaled four-field equations,  (\ref{e469})--(\ref{e473}), ensure that ${\mit\Psi}$, ${\cal V}$, and
${\cal J}$ are even functions of $X$, whereas ${\mit\Phi}$ and ${\cal N}$ are odd functions.

\subsection{Ordering Scheme}
In the following, the dimensionless parameters $\epsilon_d$, $\epsilon_\beta$, $\epsilon_n$, $\epsilon_\eta$, $\epsilon_\chi$,
and $\epsilon_D$ are all assumed to be of similar size, but much smaller than unity. The orderings $\epsilon_n\ll 1$ and $\epsilon_\beta\ll 1$
are consistent with the standard large-aspect ratio, low-$\beta$ orderings used to describe conventional tokamak
plasmas (Freidberg 1987). As will become apparent, the ordering $\epsilon_d\ll 1$ ensures that the island chain is
sufficiently wide that ion acoustic waves propagating parallel to the magnetic field are able to smooth out any
variations in the normalized electron number density, ${\cal N}$, around magnetic flux-surfaces (Scott, Hassam \& Drake 1985). The fact that $\epsilon_d\ll 1$ implies that
\begin{equation}
w \gg \rho_\beta,
\end{equation}
where
\begin{equation}
\rho_\beta = \left(\frac{L_s}{L_n}\right)d_\beta
\end{equation}
is a characteristic lengthscale that is of order the ion poloidal gyroradius. 
 The orderings $\epsilon_\eta\ll 1$, $\epsilon_\chi\ll 1$, and $\epsilon_D\ll 1$ ensure that the island
chain is sufficiently wide that the perpendicular diffusion of magnetic flux, momentum, and particles are not dominant
effects in the rescaled four-field equations. We shall also assume that $w/w_c\sim{\cal O}(1)$. In other words, the
island chain is sufficiently wide for the parallel diffusion of particles to compete with perpendicular diffusion.

@@

Finally, to lowest order in $\epsilon_d$, Equation~(\ref{e470}) yields
\begin{equation}\label{e509}
\{{\cal J}_0,{\mit\Omega}\} = -\partial_X\!\left\{{\mit\Phi}_0+\frac{{\cal N}_0}{1+\tau}, \partial_X {\mit\Phi}_0\right\}=
\frac{1}{2}\left\{d_{\mit\Omega}\!\left[M\left(M+\frac{L}{1+\tau}\right)\right]X^2, {\mit\Omega}\right\},
\end{equation}
where use has been made of Equations~(\ref{e498}), (\ref{e501}), and (\ref{e505}). Moreover, $d_{\mit\Omega}\equiv
d/d{\mit\Omega}$.

@@

\subsection{Fluid Velocities}\label{s8.6}
The flux-surface functions $M({\mit\Omega},T)$ and $L({\mit\Omega},T)$ are directly related to the lowest-order perpendicular
velocities of the various fluid species in the island rest frame. In fact, as is clear from Sections~\ref{s4.2}, \ref{s4.3}, and \ref{s8.2}, 
\begin{align}
V_\theta(x,\zeta,T) &= -\frac{r_s\,\omega_\ast}{m}\,|X|\,M({\mit\Omega},T),\\[0.5ex]
V_{\theta\,i}(x,\zeta,T)& = -\frac{r_s\,\omega_\ast}{m}\,|X|\,Y_i({\mit\Omega},T)\\[0.5ex]
V_{\theta\,e}(x,\zeta,T)& = -\frac{r_s\,\omega_\ast}{m}\,|X|\,Y_e({\mit\Omega},T),
\end{align}
where
\begin{align}
Y_i({\mit\Omega},T)&= M+\left(\frac{1}{1+\tau}\right)L,\label{e518}\\[0.5ex]
Y_e({\mit\Omega},T)&= Y_i- L.
\end{align}
Here, $V_\theta$, $V_{\theta\,i}$, and $V_{\theta\,e}$ refer to velocity components of the MHD, ion, and
electron fluid, respectively. Note that $Y_i$ and $Y_e$ are both zero inside the magnetic separatrix of the island chain.

@@

We need to evaluate Equation~(\ref{e471}) to first order in $\epsilon_d$ in order to include the perpendicular transport term. Doing so,
we obtain
\begin{equation}
0= \epsilon_d\,\{{\cal V}_1, {\mit\Omega}\} + \epsilon_D\,(X^2\,d_{\mit\Omega} L + L),
\end{equation}
where use has been made of Equations~(\ref{e498}), (\ref{e500}),  and (\ref{e501}). The flux-surface average of the
previous equation yields
\begin{equation}
\langle X^2\rangle\,d_{\mit\Omega} L +\langle 1\rangle\,L = 0,
\end{equation}
where use has been made of Equation~(\ref{e5111}). 
We can solve the previous equation, subject to the boundary condition (\ref{e502}), to give
\begin{equation}\label{e526}
L({\mit\Omega})=\left\{
\begin{array}{llr}
0&&-1\leq {\mit\Omega}\leq 1\\[0.5ex]
1/\langle X^2\rangle&~~&{\mit\Omega}>1
\end{array}\right..
\end{equation}
Here, we have taken into account the previously mentioned fact that $L=0$ within the island separatrix.
Note that $L$ is discontinuous across the island separatrix, which implies that the density gradient, and, hence,
the diamagnetic velocity, are both also discontinuous across the separatrix. Of course, there is not a real
discontinuity. Given that the discontinuity in $L$ is mandated by the ordering $\epsilon_d=(\rho_\beta/w)^2\ll 1$, which
requires $L$ to be a flux-surface function, and, hence, zero by symmetry inside the separatrix, it follows that the discontinuity is resolved by a thin layer of characteristic thickness $\rho_\beta$ on the island
separatrix.

We need to evaluate Equation~(\ref{e470}) to first order in $\epsilon_d$ in order to include the perpendicular transport term. Doing so,
we obtain
\begin{equation}\label{e528a}
0 =\epsilon_d\,\{{\cal J}_1,{\mit\Omega}\} +\epsilon_\chi\,X\,d_{{\mit\Omega}}\!\left[d_{\mit\Omega}\!\left(X^3\,d_{\mit\Omega} Y_i\right)\right].
\end{equation}
where use has been made of Equations~(\ref{e498}), (\ref{e500}), (\ref{e501}), (\ref{e503}), (\ref{e505}), and (\ref{e518}). The flux-surface average of the previous equation yields 
\begin{equation}
d_{\mit\Omega}^{\,2}\!\left(\langle X^4\rangle\,d_{\mit\Omega} Y_i\right)= 0.
\end{equation}
We can solve the previous equation, subject to the boundary conditions (\ref{e502}) and (\ref{e506}), to give
\begin{equation}\label{e530}
Y_i({\mit\Omega},T)=\frac{v'(T)}{\int_1^\infty \!\frac{d{\mit\Omega}}{\langle X^4\rangle}}\left\{
\begin{array}{llr}
0&&-1\leq {\mit\Omega}\leq 1\\[0.5ex]
\int_1^{\mit\Omega}\! \frac{d{\mit\Omega}'}{\langle X^4\rangle}&~~&{\mit\Omega}>1
\end{array}\right.
\end{equation}
(Fitzpatrick \& Waelbroeck 2005).
Here, we have rejected, as unphysical, the solution that blows up as ${\mit\Omega}^{\,1/2}$ as ${\mit\Omega}\rightarrow\infty$. 
We have also made use of the fact that $Y_i=0$ within the magnetic separatrix of the island chain. Finally, we have  demanded that the ion
fluid velocity, and, hence, the function $Y_i$,  be continuous across the separatrix, because the ion fluid possesses finite perpendicular viscosity. 
Note, however, that the discontinuity in the function $L({\mit\Omega})$ across the separatrix [see Equation~(\ref{e526})] implies that the
MHD and electron fluid velocities are  discontinuous across the separatrix. (See Section~\ref{s8.6}.) As previously
mentioned, these discontinuities are resolved in a layer of characteristic thickness $\rho_\beta$.

@@

Equations~(\ref{e528a}) and (\ref{e543}) can be combined to give (Fitzpatrick \& Waelbroeck 2005)
\begin{align}
{\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right) &=\frac{4\,\epsilon_\beta\,\epsilon_d\,\epsilon_\chi}{\hat{w}}\int_1^\infty
\left\langle X^{2}\,d_{\mit\Omega}\!\left[d_{\mit\Omega}(X^3\,d_{\mit\Omega}Y_i)\right]\right\rangle d{\mit\Omega}\nonumber\\[0.5ex]
&=\frac{4\,\epsilon_\beta\,\epsilon_d\,\epsilon_\chi}{\hat{w}}\int_1^\infty d_{\mit\Omega}\!\left(-\langle X\rangle\,Y_i
+2\,\langle X^3\rangle\,d_{\mit\Omega} Y_i + \langle X^5\rangle\,d_{\mit\Omega}^{\,2} Y_i\right)d{\mit\Omega}\nonumber\\[0.5ex]
&= \frac{4\,\epsilon_\beta\,\epsilon_d\,\epsilon_\chi}{\hat{w}}\,\lim_{\mit\Omega\rightarrow\infty}\left(-\langle X\rangle\,Y_i
+2\,\langle X^3\rangle\,d_{\mit\Omega} Y_i + \langle X^5\rangle\,d_{\mit\Omega}^{\,2} Y_i\right),
\end{align}
where use has been made of the facts that $Y_i$ is zero inside the island separatrix, and $Y_i$ is continuous across the separatrix.
Combining the previous equation with Equation~(\ref{e530}), we obtain (Fitzpatrick \& Waelbroeck 2005)
\begin{equation}\label{e545}
{\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)  =- \frac{4\,\epsilon_\beta\,\epsilon_d\,\epsilon_\chi\,v'}{\hat{w}}.
\end{equation}
The previous equation yields
\begin{equation}
\left[r\,\frac{d\omega_E}{dr}\right]_{r_{s-}}^{r_{s+}} = \left(\frac{\tau_\varphi\,\hat{w}^{\,4}}{2\,\tau_H^{\,2}}{\rm Im}\!\right)\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right),
\end{equation}
where use has been made of Equation~(\ref{e489}). The same relation can be obtained by integrating Equation~(\ref{e182}) across the resonant surface, making use of Equation~(\ref{e157}), as well as the
identification
\begin{equation}
\left[r\,\frac{d\omega_E}{dr}\right]_{r_{s-}}^{r_{s+}} = m\left[r\,\frac{\partial{\mit\Delta\Omega}_\theta}{\partial r}\right]_{r_{s-}}^{r_{s+}}.
\end{equation}
The latter result merely states that the  discontinuity in the MHD fluid velocity gradient that develop at the resonant
surface is mirrored by an equal discontinuity in the ion fluid velocity gradient (because the discontinuity is ultimately due to 
a discontinuity in the ${\bf E}\times {\bf B}$ velocity gradient).

Equations~(\ref{e524a}) and (\ref{e542}) can be combined to give
\begin{align}
{\rm Re}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)&= \frac{2\,\epsilon_\beta\,\epsilon_d}{\hat{w}}
\int_{1+}^\infty d_{\mit\Omega}(M\,Y_i)\left\langle\widetilde{X^2}\,\cos\zeta\right\rangle d{\mit\Omega}
+\frac{4}{\epsilon_\eta\,\hat{w}}\,\frac{d(\ln \hat{w}^2)}{dT}\int_{-1}^\infty \frac{\langle \cos\zeta\rangle^2}{\langle 1\rangle}\,d{\mit\Omega}
\end{align}
Making use of Equations~(\ref{e518}), (\ref{e526}), and (\ref{e530}), the previous equation yields
\begin{align}
{\rm Re}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)&= -\frac{2\,\epsilon_\beta\,\epsilon_d\,v'}{(1+\tau)\,\hat{w}}
\int_1^\infty d_{\mit\Omega}\!\left(\frac{F_i}{\langle X^2\rangle}\right)\left\langle\widetilde{X^2}\,\cos\zeta\right\rangle d{\mit\Omega}
\nonumber\\[0.5ex]
&\phantom{=}+ \frac{2\,\epsilon_\beta\,\epsilon_d\,v'^{\,2}}{\hat{w}} \,\int_1^\infty d_{\mit\Omega}\!\left(F_i^{\,2}\right)\left\langle\widetilde{X^2}\,\cos\zeta\right\rangle d{\mit\Omega}\nonumber\\[0.5ex]
&\phantom{=}+\frac{4}{\epsilon_\eta\,\hat{w}}\,\frac{d(\ln \hat{w}^2)}{dT}\int_{-1}^\infty \frac{\langle \cos\zeta\rangle^2}{\langle 1\rangle}\,d{\mit\Omega},\label{e547}
\end{align}
where
\begin{equation}
F_i({\mit\Omega})=\left.\int_1^{\mit\Omega}\frac{d{\mit\Omega}'}{\langle X^4\rangle}\right/\int_1^\infty\frac{d{\mit\Omega}}{\langle X^4\rangle}
\end{equation}
Finally, Equations~(\ref{e545}) and (\ref{e547})
can be combined to give (Waelbroeck \& Fitzpatrick 1997; Fitzpatrick \& Waelbroeck 2005a)
\begin{align}\label{e559}
{\rm Re}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)&= I_1\,\tau_R\,\frac{d}{dt}\!\left(\frac{4\,w}{r_s}\right)
- I_2\left(\frac{c_\beta}{1+\tau}\right)\left(\frac{\rho_\beta}{r_s}\right)\left(\frac{\tau_\varphi}{\tau_H}\right)\left(\frac{w}{r_s}\right)^2 {\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)\nonumber\\[0.5ex]
&\phantom{=} -I_3\left(\frac{\tau_\varphi}{\tau_H}\right)^2 \left(\frac{w}{r_s}\right)^7\left[{\rm Im}\!\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right)\right]^2, 
\end{align}
where
\begin{align}
I_1 &= 2\int_{-1}^\infty \frac{\langle \cos\zeta\rangle^2}{\langle 1\rangle}\,d{\mit\Omega} =0.8227,\\[0.5ex]
I_2&= \frac{1}{4}\int_1^\infty d_{\mit\Omega}\!\left(\frac{F_i}{\langle X^2\rangle}\right)\left(\langle X^4\rangle - \frac{\langle X^2\rangle^2}{\langle 1\rangle}\right)d{\mit\Omega} =4.889\times 10^{-2},\\[0.5ex]
I_3&= \frac{1}{16}\int_1^\infty d_{\mit\Omega}\!\left(F_i^{\,2}\right)\left(\langle X^4\rangle - \frac{\langle X^2\rangle^2}{\langle 1\rangle}\right)d{\mit\Omega} =2.944\times 10^{-2}.
\end{align}
Here, use has been made of Equations~(\ref{e317a}), (\ref{e318a}), (\ref{e481}), and (\ref{e482}).

\section{Isolated Magnetic Island Chain}
\subsection{Introduction}
Suppose that the wall surrounding the plasma is perfectly conducting (i.e.\, $\tau_w\rightarrow\infty$), and that there is no current
flowing through the external magnetic-field coil (i.e., $\hat{I}_c=0$). In this case, assuming that $d/dt = -{\rm i}\,\omega$, Equations~(\ref{e202}), 
(\ref{e203}), and (\ref{epw}),  yield 
\begin{equation}\label{e563}
\left(\frac{{\mit\Delta}\hat{\mit\Psi}_s}{\hat{\mit\Psi}_s}\right) ={\mit\Delta}_{pw},
\end{equation}
where ${\mit\Delta}_{pw}$ is the (real) perfect-wall tearing stability index.
